\\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2021-11-10 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.Rmd
do not compare cases and bases

As discussed in Hanley & Miettinen [-@hanley2009fitting], the key idea behind case-base sampling is to consider the entire study base as an infinite collection of *person-moments*. These person-moments are indexed by both an individual in the study and a time point, and therefore each person-moment has a covariate profile, an exposure status, and an outcome status (i.e. whether the event happened) attached to it. By comparing person-moments at which an event occurred with person-moments at which no event occurred, we can extract information about hazards and survival.

@@

  1. Compute $\hat{\theta}$ and its variance-covariance matrix $V(\theta)$.
  2. Sample $B$ times from a multivariate normal $N\left(\hat{\theta}, V(\theta)\right)$.
  3. For each sample, compute the survival function using Equation \ref{eqn:surv} below.
  4. Use the pointwise quantiles of these survival function estimates to construct a pointwise confidence band for the survival function.

>>>>

As discussed in Hanley & Miettinen [-@hanley2009fitting], the key idea behind case-base sampling is to consider the entire study base as an infinite collection of *person-moments*. These person-moments are indexed by both an individual in the study and a time point, and therefore each person-moment has a covariate profile, an exposure status, and an outcome status (i.e. whether the event happened) attached to it. By estimating the probability of an event occurring at a particular person-moment, we can extract information about hazards and survival.

@@

  1. Compute $\hat{\theta}$ and its variance-covariance matrix $V(\theta)$.
  2. Sample $B$ times from a multivariate normal $N\left(\hat{\theta}, V(\theta)\right)$.
  3. For each sample, compute the survival function using Equation \ref{eqn:surv} below.
  4. Use the pointwise quantiles of these survival function estimates to construct a pointwise confidence band for the survival function of interest.
